### 2020-03-07 short.body.tex
tweaking stuff

@@

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}\\
\mbox{}\\
\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Relevance of asymptomatic transmission given variation in
probability that a given, newly infected individual is asymptomatic. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
(C) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(D) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
For panels A--B, we vary relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, while assuming $\kappa_a = \kappa_s$.
For panels C--D, we vary relative generation-interval dispersion of asymptomatic cases, $\kappa_a/\kappa_s$, while assuming $G_a = G_s$.
As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.
% Technically, renewal equations provide a route to connect
% observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
% where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
% For the present model,
% $M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
% where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
% $M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
% $M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
% and $q$ is the fraction of realized new secondary cases caused by
% asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
% $\gamma_s=1/10$, and $r=1/7$. Here, the average duration
% in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
% $T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
% in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
% $p=0.5$ and $p=0.9$ for reference.
%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and 
%$M(r)$ is related to 
%$g(a)$ (the normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. 
%The relevance $q$ is an unknown feature of
\label{fig.relevance}}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
(C) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(D) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
Here, we vary relative mean generation interval of asymptomatic cases, $\bar G_a/\bar G_s$, while assuming $\kappa_a = \kappa_s$.
As our baseline parameters, we assume $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$.
\label{fig.relevance}}
\end{center}
\end{figure*}

@@
